Inferring community characteristics in labelled networks

### 2021-05-25 nips/additional.tex
Lines on graphs

\subsection{Initializing the b-chain}

>>>>

By way of illustration, we can consider the primary school dataset \cite{schools}. We plot the normalised objective function $U\left( \theta^{(t)} \right) / N$ with respect to MALA iteration on figure \ref{fig:school-U-orginal}. We see that the chain converges to the modal neighbourhood quickly (within about 2000 iterations of a total 10,000). Nevertheless, we pick $\kappa_\theta=0.4 > 0.2$ just to be on the safe-side. $\lambda_\theta=10$ is chosen somewhat arbitrarily as we do not require neighbouring samples to be independent. Nevertheless, this thinning does speed up computation of quantities that require an average over all the retained samples -- as $|\Tcal_\theta| < T_\theta$.
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.4\linewidth}
		\centering
		\includegraphics[width=\linewidth]{school-U-original.png}
		\caption{Original samples $t \in [T_\theta]$}
		\label{fig:school-U-orginal}
	\end{subfigure}
	\begin{subfigure}[t]{0.4\linewidth}
		\centering
		\includegraphics[width=\linewidth]{school-U-thinned.png}
		\caption{Thinned samples $t \in \Tcal_\theta$ indexed by $i$}
		\label{fig:school-U-thinned}
	\end{subfigure}
	\hspace{1cm}
	\caption{Primary school dataset normalised objective function against sample index}
\end{figure}

We see on figure \ref{fig:school-U-thinned} that $U(\theta^{(i)})$ does bounce around a small amount. This is to be expected we are sampling from the posterior rather than converging to the MAP. The variations do appear to be rather long in time-scale but we can live with this as we do not require sample independence.
\FloatBarrier
\subsection{Initializing the b-chain}
